\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[all]{xy}


\usepackage{amsmath,amsthm,amssymb,color,latexsym}
\usepackage{geometry}        
\geometry{letterpaper}    
\usepackage{graphicx}

\newtheorem{problem}{}

\newenvironment{solution}[1][\it{Solution}]{\textbf{#1. } }{$\square$}


\begin{document}
\noindent Data Science for Economist section Spring 2024\hfill Problem Set \#2.\\
Emilien Akotenou. (Ph.D Student, OU)

\hrulefill


\begin{section}{Big data tools}
Measurement
Statistical programming languages
Visualization tools (usually included with the above)
Big Data management software
Data collection tools

\begin{subsection}{Measurement }
   
\end{subsection} 
\begin{subsection}{Statistical programming languages}
Three main programming languages are widely used for data manipulation, analysis:R, Python and Julia.  
\end{subsection} 
\begin{subsection}{Data collection, Cleaning and Preprocessing}
Web Scraping can be done in almost any programming language out there
Handling large data sets with RDD.  To use RDDs you need a cluster of computers and software such as Hadoop or Spark. \newline
 OpenRefine: Tool for cleaning and transforming data. \newline
scikit-learn, caret: Libraries for data preprocessing in machine learning.  
\end{subsection} 
\begin{subsection}{Version Control}
Git and GitHub: Distributed version control system.   
\end{subsection} 
\begin{subsection}{Cloud Computing Platforms}
AWS, Azure, Google Cloud: Cloud platforms that provide scalable computing resources.   
\end{subsection}

\begin{subsection}{Data Manipulation and Analysis}
Pandas: Python library for data manipulation and analysis. \newline
NumPy: Fundamental package for scientific computing with Python. \newline
dplyr: R package for data manipulation and transformation.  \newline
SQL : To transform data into a more usable form for statistical software to use. With SQL, one can easily subset, merge, and perform other common data transformations.
\end{subsection}

\begin{subsection}{Data Visualization}
Allows humans to see in multiple dimensions what the data looks like, spot outliers, and otherwise perform "sanity checks" on the data. \newline
Matplotlib: Python 2D plotting library. \newline
ggplot2: package included in the R tidyverse for creating complex and customizable plots.
\end{subsection}

\begin{subsection}{Modeling}
The main objectives of statistical modeling are as follows: \newline
Use the data to test theories. \newline
Use the data to predict behavior. \newline
Use the data to explain behavior. 
\end{subsection}

\end{section}


 
\end{document}
